---
title: "AI Analytics 3 - Risk Prediction"
author: Alex
date: '2018-02-26'
slug: ai-analytic-03
categories:
  - AI
  - R
tags:
  - AI
  - analysis
  - machine learning
  - plot
  - R
  - regression
  - R Markdown
  - visualization
---

### Read in data and functions
```{r}
source("2018-02-21-ai-analytics/BDVis.R")
source("2018-02-21-ai-analytics/UniVarAnal.R")
source("2018-02-21-ai-analytics/RiskPrediction.R")
mdl.data<-readRDS("2018-02-21-ai-analytics/mdl.data.RDS")
mdl.strct<-readRDS("2018-02-21-ai-analytics/mdl.strct.RDS")
#saveRDS(mdl.data,"2018-02-21-ai-analytics/mdl.data.RDS")
#saveRDS(mdl.strct,"2018-02-21-ai-analytics/mdl.strct.RDS")
```



## Regression
```{r}
mdl.glm<-log.reg(mdl.data)
coef.proc.df<-coef.proc(summary(mdl.glm)$coef)
coef.proc.df<-coef.intpt(coef.proc.df,mdl.data,mdl.strct)
summary(mdl.glm)
```

## Coefficient
### R coefficient with knitr
```{r}
coef.df.to.kable(coef.proc.df)
```

### Visualizing coefficients
```{r}
reg.cat.vis("Race",coef.proc.df,trend=F)
reg.cat.vis("Marital",coef.proc.df,trend=F)
reg.cat.vis("DiabetesYear",coef.proc.df)
reg.cat.vis("BMI",coef.proc.df)
reg.cat.vis("HbA1c",coef.proc.df)
reg.cat.vis("BP",coef.proc.df)
reg.cat.vis("LDL",coef.proc.df)
```


### Parallel variable visualization
This horizontal bar-chart is suitable for presenting the effects of a series of binomial variable
```{R}
para.coef.df<-coef.proc.df[coef.proc.df$VarGrp=="Comorbidity & Complication",]
para.coef.df<-para.coef.df[rev(order(para.coef.df$Variable)),]
reg.para.var.vis(para.coef.df,"Comorbidity & Complication")
```


## Model validation

### Prediction score
```{R,warnings=F}
mdl.pred<-pred.score.fun(mdl.glm,mdl.data)
pred.score.dist.vis(mdl.pred)
```


### ROC & AUC
```{R}
roc.vis(mdl.pred)
```


### Fitting performance
```{R,fig.width=12,fit.height=6}
perf.sum.vis(mdl.pred)
```


### Fitting performance
```{R,width=10}
threshold.sel.vis(mdl.pred)
```


### Lift
How much better if using the prediction compare to pure guess
```{R}
perf.vis(mdl.pred,"lift")
```






















