---
title: "AI Analytics 1 - Overview of Dataset"
author: "Alex"
date: '2018-02-21'
slug: ai-analytics
tags:
- analysis
- visualization
- regression
- machine learning
- AI
categories:
- R
- AI
---


Read in data and functions
```{r}
source("2018-02-21-ai-analytics/BDVis.R")
CH1.demo<-readRDS("2018-02-21-ai-analytics/CH1.demo.RDS")
```

### Visualization procedure:
1. Use the column name to quote the column, aggregate the column, see function col.aggr
2. Rename, reorder the column, if necessary
3. Use the appropriate Visualization function to plot.



Visualization code
```{R}
#Age distribution
vis.age<-age.vis(CH1.demo[,getcolumn("age",CH1.demo)])


#Gender distribution
cat.df<-col.aggr("gender",CH1.demo)
vis.gender<-cat.vis(cat.df,Title="Gender")


#Race distribution
cat.df<-col.aggr("Race",CH1.demo)
cat.df<-cat.df[c(1,3,2,4),]
vis.race<-cat.vis(cat.df,Title="Ethnicity")


#Marital status distribution
cat.df<-col.aggr("marital",CH1.demo)
cat.df$Var1[1]<-"Devorced"
cat.df<-cat.df[c(3,2,1,5,4),]
vis.marital<-cat.vis(cat.df,Title="Marital Status")


#Medifund distribution
cat.df<-col.aggr("mediFundHx",CH1.demo)
cat.df$Var1<-c("No","Yes")
cat.df<-cat.df[2:1,]
vis.medifund<-cat.vis(cat.df,Title="MediFund")



#Diabetes year distribution
cat.df<-col.aggr("Diabetes_year",CH1.demo)
cat.df<-cat.df[c(1,3:5,2),]
vis.diab.yr<-cat.vis(cat.df,Title="Diabetes Year")


#Patient type distribution
cat.df<-col.aggr("PAT_TYPE",CH1.demo)
vis.pat_type<-cat.vis(cat.df,Title="Patient type")



#Disease Prevalence
prev.df<-cols.aggr(CH1.demo[8:19])
prev.df$Disease[c(7,11,12)]<-c("Heart Failure","Major Amputation","Minor Amputation")
prev.df<-df.sort(prev.df)
vis.prev<-Prev.vis(prev.df)
```


## Individual Visualization

Age distribution
```{r,echo = FALSE}
vis.age

```

Gender distribution
```{r,echo = FALSE}
vis.gender
```

Race distribution
```{r,echo = FALSE}
vis.race
```

Marital status distribution
```{r,echo = FALSE}
vis.marital
```

Medifund distribution
```{r,echo = FALSE}
vis.medifund
```


Diabetes year distribution
```{r,echo = FALSE}
vis.diab.yr
```

Patient type distribution
```{r,echo = FALSE}
vis.pat_type
```


Disease Prevalence
```{r,echo = FALSE}
vis.prev
```




## Dashboard
### Demographic
```{r,fig.asp = 1.2,fig.width=10}
grid.arrange(vis.age,vis.gender,vis.race,vis.marital,layout_matrix=matrix(1:4,2,2,byrow=T))
```


Disease related history
```{r,fig.asp = 1.2,fig.width=10}
grid.arrange(vis.diab.yr,vis.medifund,vis.pat_type,layout_matrix=matrix(c(1,1,2,3),2,2,byrow=T))
```


Disease prevalence
```{r}
vis.prev
```

















