---
title: "AI Analytics 1 - Overview of Dataset"
author: "Alex"
date: '2018-02-21'
slug: ai-analytics
tags:
- analysis
- visualization
- regression
- machine learning
- AI
categories:
- R
- AI
---


Read in data and functions
```{r}
source("2018-02-21-ai-analytics/BDVis.R")
CH1.demo<-readRDS("2018-02-21-ai-analytics/CH1.demo.RDS")
```

### Visualization procedure:
1. Use the column name to quote the column, aggregate the column, see function col.aggr
2. Rename, reorder the column, if necessary
3. Use the appropriate Visualization function to plot.



Visualization code
```{R}
#Age distribution
vis.age<-age.vis(CH1.demo[,getcolumn("age",CH1.demo)])


#Gender distribution
cat.df<-col.aggr("gender",CH1.demo)
vis.gender<-cat.vis(cat.df,Title="Gender")


#Race distribution
cat.df<-col.aggr("Race",CH1.demo)
cat.df<-cat.df[c(1,3,2,4),]
vis.race<-cat.vis(cat.df,Title="Ethnicity")


#Marital status distribution
cat.df<-col.aggr("marital",CH1.demo)
cat.df$Var1[1]<-"Devorced"
cat.df<-cat.df[c(3,2,1,5,4),]
vis.marital<-cat.vis(cat.df,Title="Marital Status")


#Medifund distribution
cat.df<-col.aggr("mediFundHx",CH1.demo)
cat.df$Var1<-c("No","Yes")
cat.df<-cat.df[2:1,]
vis.medifund<-cat.vis(cat.df,Title="MediFund")



#Diabetes year distribution
cat.df<-col.aggr("Diabetes_year",CH1.demo)
cat.df<-cat.df[c(1,3:5,2),]
vis.diab.yr<-cat.vis(cat.df,Title="Diabetes Year")


#Patient type distribution
cat.df<-col.aggr("PAT_TYPE",CH1.demo)
vis.pat_type<-cat.vis(cat.df,Title="Patient type")



#Disease Prevalence
prev.df<-cols.aggr(CH1.demo[8:19])
prev.df$Disease[c(7,11,12)]<-c("Heart Failure","Major Amputation","Minor Amputation")
prev.df<-df.sort(prev.df)
vis.prev<-Prev.vis(prev.df)
```


## Initial slides for auto-generation
```{r,echo = FALSE}
require("ReporteRs")
mysld<-pptx("Overview of Dataset","2018-02-21-ai-analytics/template.pptx")%>%
  addSlide("Title Slide")%>%
  addTitle("Overview of Dataset")
```

## Individual Visualization

Age distribution
```{r,echo = FALSE}
vis.age+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Age Distribution")%>%
  addPlot(function(x)print(vis.age))
```

Gender distribution
```{r,echo = FALSE}
vis.gender
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Gender Distribution")%>%
  addPlot(function(x)print(vis.gender))
```

Race distribution
```{r,echo = FALSE}
vis.race+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Ethnicity Distribution")%>%
  addPlot(function(x)print(vis.race))
```

Marital status distribution
```{r,echo = FALSE}
vis.marital+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Marital Status Distribution")%>%
  addPlot(function(x)print(vis.marital))
```

Medifund distribution
```{r,echo = FALSE}
vis.medifund
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("MediFund Distribution")%>%
  addPlot(function(x)print(vis.medifund))
```


Diabetes year distribution
```{r,echo = FALSE}
vis.diab.yr+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Diabetes History Distribution")%>%
  addPlot(function(x)print(vis.diab.yr))
```

Patient type distribution
```{r,echo = FALSE}
vis.pat_type+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Patient Type (NHGP/TTSH) Distribution")%>%
  addPlot(function(x)print(vis.pat_type))
```


Disease Prevalence
```{r,echo = FALSE}
vis.prev+wm
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Disease Prevalence Distribution")%>%
  addPlot(function(x)print(vis.prev))
```




## Dashboard
### Demographic
```{r,fig.asp = 1.2,fig.width=10}
#arrangeGrob(grobs=list(vis.age,vis.gender,vis.race,vis.marital),layout_matrix=matrix(1:4,2,2,byrow=T),height=800,width=900)%>%grid.draw
grid.arrange(vis.age,vis.gender,vis.race,vis.marital+wm,layout_matrix=matrix(c(1,1,1,1,2,2,3,3,3,4,4,4),2,6,byrow=T))
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Dashboard - Demographics")%>%
  addPlot(function(x)grid.arrange(vis.age,vis.gender,vis.race,vis.marital,layout_matrix=matrix(c(1,1,1,1,2,2,3,3,3,4,4,4),2,6,byrow=T)),vector.graphic=F,offx=1.7,offy=.9,width=6.5,height=6.5)
```


Medical history
```{r,fig.asp = 1.2,fig.width=10}
grid.arrange(vis.diab.yr,vis.medifund,vis.pat_type,layout_matrix=matrix(c(1,1,2,3),2,2,byrow=T))
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Dashboard - Medical History")%>%
  addPlot(function(x)grid.arrange(vis.diab.yr,vis.medifund,vis.pat_type,layout_matrix=matrix(c(1,1,2,3),2,2,byrow=T)),vector.graphic=F,offx=1.7,offy=.9,width=6.5,height=6.5)
```


Disease prevalence
```{r}
vis.prev
mysld<-addSlide(mysld,"Title and Content")%>%
  addTitle("Dashboard - Disease Prevalence")%>%
  addPlot(function(x)print(vis.prev))
```


Write Slides for Download
```{r}
writeDoc(mysld,"Overview of Dataset.pptx")
```

[Download]("Overview of Dataset.pptx") the summary slides












