---
title: ai-analytic-04
author: Alex
date: '2018-03-06'
slug: ai-analytic-04
categories:
  - AI
  - R
tags:
  - AI
  - analysis
  - machine learning
  - plot
  - R Markdown
  - R
  - regression
  - visualization
---


```{r}
source("2018-02-21-ai-analytics/BDVis.R")
source("2018-02-21-ai-analytics/UniVarAnal.R")
source("2018-02-21-ai-analytics/RiskPrediction.R")
CH1.demo<-readRDS("2018-02-21-ai-analytics/CH1.demo.RDS")
CH1.out<-readRDS("2018-02-21-ai-analytics/CH1.out.RDS")
pat.grp<-CH1.out[,1:2]
pat.grp$Death<-sapply(as.character(pat.grp$Death),function(x)switch(x,"0"="Alive","1"="Death"))
names(pat.grp)[2]<-"group"
CH1.demo<-left_join(CH1.demo,pat.grp)

mdl.strct<-readRDS("2018-02-21-ai-analytics/mdl.strct.RDS")
mdl.data<-readRDS("2018-02-21-ai-analytics/mdl.data.RDS")

#########################################################################
# Overview of dataset
#########################################################################

#Age distribution
vis.age<-age.vis(CH1.demo[,getcolumn("age",CH1.demo)])


#Gender distribution
cat.df<-col.aggr("gender",CH1.demo)
vis.gender<-cat.vis(cat.df,Title="Gender")


#Race distribution
cat.df<-col.aggr("Race",CH1.demo)
cat.df<-cat.df[c(1,3,2,4),]
vis.race<-cat.vis(cat.df,Title="Ethnicity")


#Marital status distribution
cat.df<-col.aggr("marital",CH1.demo)
cat.df$Var1[1]<-"Devorced"
cat.df<-cat.df[c(3,2,1,5,4),]
vis.marital<-cat.vis(cat.df,Title="Marital Status")


#Medifund distribution
cat.df<-col.aggr("mediFundHx",CH1.demo)
cat.df$Var1<-c("No","Yes")
cat.df<-cat.df[2:1,]
vis.medifund<-cat.vis(cat.df,Title="MediFund")



#Diabetes year distribution
cat.df<-col.aggr("Diabetes_year",CH1.demo)
cat.df<-cat.df[c(1,3:5,2),]
vis.diab.yr<-cat.vis(cat.df,Title="Diabetes Year")


#Patient type distribution
cat.df<-col.aggr("PAT_TYPE",CH1.demo)
vis.pat_type<-cat.vis(cat.df,Title="Patient type")



#Disease Prevalence
prev.df<-cols.aggr(CH1.demo[8:19])
prev.df$Disease[c(7,11,12)]<-c("Heart Failure","Major Amputation","Minor Amputation")
prev.df<-df.sort(prev.df)
vis.prev<-Prev.vis(prev.df)



#########################################################################
# Data Comparison by Outcome
#########################################################################

#Age distribution
vis.age.comp<-age.vis(CH1.demo[,getcolumn("age|group",CH1.demo)])
tab.age.comp<-coef.temp.func(CH1.demo,"age|group")


#Gender distribution
cat.df<-col.aggr("gender|group",CH1.demo)
vis.gender.comp<-cat.vis(cat.df,Title="Gender")
tab.gender.comp<-coef.temp.func(CH1.demo,"gender|group")


#Race distribution
cat.df<-col.aggr("Race|group",CH1.demo)
vis.race.comp<-cat.vis(cat.df,Title="Ethnicity")
tab.race.comp<-coef.temp.func(CH1.demo,"race|group")


#Marital status distribution
cat.df<-col.aggr("marital|group",CH1.demo)
cat.df[c(1,6),1]<-"Devorced"
vis.marital.comp<-cat.vis(cat.df,Title="Marital Status")
tab.marital.comp<-coef.temp.func(CH1.demo,"marital|group")


#Medifund distribution
cat.df<-col.aggr("mediFundHx|group",CH1.demo)
cat.df[,1]<-rep(c("No","Yes"),2)
vis.medifund.comp<-cat.vis(cat.df,Title="MediFund")
tab.medifund.comp<-coef.temp.func(CH1.demo,"mediFundHx|group")



#Diabetes year distribution
cat.df<-col.aggr("Diabetes_year|group",CH1.demo)
cat.df$Diabetes_year<-factor(cat.df$Diabetes_year,levels=cat.df[c(1,3:5,2),1])
vis.diab.yr.comp<-cat.vis(cat.df,Title="Diabetes Year")
tab.diab.yr.comp<-coef.temp.func(CH1.demo,"Diabetes_year|group")


#Patient type distribution
cat.df<-col.aggr("PAT_TYPE|group",CH1.demo)
vis.pat_type.comp<-cat.vis(cat.df,Title="Patient type")
tab.pat_type.comp<-coef.temp.func(CH1.demo,"PAT_TYPE|group")



#Disease Prevalence
demo.sub<-CH1.demo[,c(8:19,22)]
names(demo.sub)[c(7,11,12)]<-c("Heart Failure","Major Amputation","Minor Amputation")
prev.df<-cols.aggr(demo.sub)
prev.df<-df.sort(prev.df)
vis.prev.comp<-Prev.vis(prev.df)
```


## Data Overview

### Demographics

```{R,fig.asp = .85,fig.width=10,echo = FALSE,message=F}
grid.arrange(vis.age,vis.gender,vis.race,vis.marital,layout_matrix=matrix(c(1,1,1,1,2,2,3,3,3,4,4,4),2,6,byrow=T))
```

### Medical History

```{R,fig.asp = 1.2,fig.width=8,echo = FALSE,message=F}
grid.arrange(vis.diab.yr,vis.medifund,vis.pat_type,layout_matrix=matrix(c(1,1,2,3),2,2,byrow=T))
```

Disease prevalence
```{r,echo = FALSE,message=F}
vis.prev
```

## Comparison by Ouctome

### Demographics

```{R,fig.asp = .85,fig.width=10,echo = FALSE,message=F}
grid.arrange(vis.age.comp,vis.gender.comp,vis.race.comp,vis.marital.comp,layout_matrix=matrix(c(1,1,1,1,2,2,3,3,3,4,4,4),2,6,byrow=T))
```



### Medical History

```{R,fig.asp = 1.2,fig.width=8,echo = FALSE,message=F}
grid.arrange(vis.diab.yr.comp,vis.medifund.comp,vis.pat_type.comp,layout_matrix=matrix(c(1,1,2,3),2,2,byrow=T))
```

Disease prevalence
```{r,echo = FALSE,message=F}
vis.prev.comp
```

## Regression Analysis

```{R,echo=F,message=F}
mdl.glm<-log.reg(mdl.data)
coef.proc.df<-coef.proc(summary(mdl.glm)$coef)
coef.proc.df<-coef.intpt(coef.proc.df,mdl.data,mdl.strct)
mdl.pred<-pred.score.fun(mdl.glm,mdl.data)
```

### Coefficients

```{R,echo=F,message=F}
coef.df.to.kable(coef.proc.df)
```

### Visualization of Coefficient

```{R,echo=F,message=F}
reg.cat.vis("DiabetesYear",coef.proc.df)
reg.cat.vis("BMI",coef.proc.df)
reg.cat.vis("HbA1c",coef.proc.df)
reg.cat.vis("BP",coef.proc.df)
reg.cat.vis("LDL",coef.proc.df)
para.coef.df<-coef.proc.df[coef.proc.df$VarGrp=="Comorbidity & Complication",]
para.coef.df<-para.coef.df[rev(order(para.coef.df$Variable)),]
reg.para.var.vis(para.coef.df,"Comorbidity & Complication")
```

## Model Validation

### Prediction Score Distribution

```{R,echo=F,message=F}
pred.score.dist.vis(mdl.pred)
```

### ROC & AUC

```{R,echo=F,message=F}
roc.vis(mdl.pred)
```


### Fitting performance

```{R,fig.width=12,fit.height=6,echo=F,message=F}
perf.sum.vis(mdl.pred)
```


### Fitting performance

```{R,width=10,echo=F,message=F}
threshold.sel.vis(mdl.pred)
```


### Lift

How much better if using the prediction compare to pure guess
```{R,echo=F,message=F}
perf.vis(mdl.pred,"lift")
```











